\textit{Supplemental figures for}: A Gaussian process model of human electrocorticographic data

### 2020-03-13 paper/supporting_information.tex

\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of full-brain correlation matrices across
    patients.}  We estimated full-brain correlation matrices
  ($\bar{K}$) using different subsets of patients from each
  dataset. We explored how stable these estimates were as a function
  of how many patients were used to compute $\bar{K}$. For each sample
  size $n$ (number of patients), we drew two non-overlapping sets of
  $n$ patients (without replacement) from the full set of patients in
  each dataset. We then estimated $\bar{K}$ using the two sets of $n$
  patients.  We computed the correlation between the upper triangles
  of these matrices as a measure of how similar the matrices were.  We
  repeated this procedure 500 times for each value of $n$ (ranging
  from 1 up to $\frac{1}{2}$ of the total number of patients in the
  given dataset); this yielded a distribution of correlation
  coefficients for each value of $n$.  Panels \textbf{A} and
  \textbf{C} display the mean correlations as a function of $n$ for
  Datasets 1 and 2, respectively.  The error ribbons denote 95\%
  confidence intervals (computed across iterations).  Panels
  \textbf{B} and \textbf{D} display the standard error of the mean
  (SEM) of these distributions of correlations as a function of $n$,
  for Datasets 1 and 2, respectively.  The error ribbons denote
  bootstrap-derived 95\% confidence intervals.}
\label{fig:supplemental_8}
\end{figure}

>>>>

\begin{figure}[p]
\centering \includegraphics[width=\textwidth]{figs/supplemental_8}
\caption{\textbf{Stability of full-brain correlation matrices across
    patients.}  We estimated full-brain correlation matrices
  ($\hat{K}$) using different subsets of patients from each
  dataset. We explored how stable these estimates were as a function
  of how many patients were used to compute $\hat{K}$. For each sample
  size $n$ (number of patients), we drew two non-overlapping sets of
  $n$ patients (without replacement) from the full set of patients in
  each dataset. We then estimated $\hat{K}$ using the two sets of $n$
  patients.  We computed the correlation between the upper triangles
  of these matrices as a measure of how similar the matrices were.  We
  repeated this procedure 500 times for each value of $n$ (ranging
  from 1 up to $\frac{1}{2}$ of the total number of patients in the
  given dataset); this yielded a distribution of correlation
  coefficients for each value of $n$.  Panels \textbf{A} and
  \textbf{C} display the mean correlations as a function of $n$ for
  Datasets 1 and 2, respectively.  The error ribbons denote 95\%
  confidence intervals (computed across iterations).  Panels
  \textbf{B} and \textbf{D} display the standard error of the mean
  (SEM) of these distributions of correlations as a function of $n$,
  for Datasets 1 and 2, respectively.  The error ribbons denote
  bootstrap-derived 95\% confidence intervals.}
\label{fig:supplemental_8}
\end{figure}
